%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\scshape Swarom Saurabh Muley} \\ \vspace{1pt}
    \small \ +1 (657)-642-8396  $\vert$  \href{mailto:smuley@scu.edu}{smuley@scu.edu} $\vert$ Santa Clara, CA  $\vert$
    \href{https://www.linkedin.com/in/swarom-muley/}{{linkedin.com/in/swarom-muley}} $\vert$ 
    \href{https://github.com/OneUpWallStreet}{github.com/OneUpWallStreet}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Santa Clara University}{Sep. 2023 -- June 2025}
      {Master of Science in Computer Science \& Engineering}{Santa Clara, CA}

    \resumeSubheading
      {Vishwakarma Institute of Technology}{Aug. 2019 -- May 2023}
      {Bachelor of Technology in Computer Engineering}{Pune, MH}
  \resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
    %\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-5pt, parsep=3pt]
                \item\small Data Structures
                \item Machine Learning
                \item Compiler Design
                \item Operating Systems
                \item Artificial Intelligence
                \item Data Science
                \item Database Management
                \item Software Engineering
                \item System Software
                \item Web Technologies
                \item Computer Networks
                \item Algorithms  
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Johnson Controls International}{Aug. 2022 -- June 2023}
      {Site Reliability Engineer Intern}{Pune, MH}
      \resumeItemListStart
        \resumeItem{Engineered a streamlined system to automate VPN access provisioning for the entire engineering organization, and seamlessly integrated it with Jira.}
        \resumeItem{Eliminated the need for manual intervention by designing a fully automated solution that handled both VPN provisioning and access removal, in addition to providing real-time status updates through email notifications using SendGrid API.}
        \resumeItem{Demonstrated efficiency as the system successfully processed thousands of VPN access requests each month, while also swiftly addressing and resolving over 5,000 Jira tickets within a short timeframe.}
        \resumeItem{Recognized for contributions to the project during the SRE all-hands meeting, highlighting the impact and effectiveness of the automated system in improving workflow and productivity.}
        \resumeItem{Contributed to a team effort in implementing MLOps practices to train a machine learning model on thousands of
hourly-generated infrastructure health tickets, facilitating automated self-healing based on categorized recurring issues.}
        \resumeItem{Automated SAAS token renewal and updates within Azure App Service across 10+ regions and environments. The system executed updates in live, operational environments and incorporated comprehensive error-handling mechanisms.}
        \resumeItem{Led Knowledge Transfer sessions for new engineers on managing and enhancing systems I developed, ensuring a smooth transition and continued operational excellence.}
      \resumeItemListEnd

    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{iOS App, Brooklyn GRE \& SAT Preparation} $|$ \emph{Swift, Python, SwiftUI, UIKit, Go, AWS, DynamoDB}}{April 2022}
          \resumeSubItem{Link - \href{https://apps.apple.com/in/app/brooklyn-gre-sat-preparation/id1620017367}{\textit{https://apps.apple.com/in/app/brooklyn-gre-sat-preparation/id1620017367}}}
          \resumeItemListStart
            \resumeItem{Built an iOS application for standardized test preparation, harnessing Swift and Golang. The backend was engineered using Golang Gin, containerized through AWS Fargate, and directed through an AWS Load Balancer over HTTPS.}
            \resumeItem{Employed a blend of SwiftUI and UIKit to create the user interface for the mobile application. Utilized Swift.SQLite for persistent data storage and integrated MixPanel for comprehensive analytics.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{iOS App, Thaleia Music Updates} $|$ \emph{Swift, Python, SwiftUI, Spotify-API, AWS SNS, MongoDB}}{Aug. 2021}
        \resumeSubItem{Link - \href{https://apps.apple.com/in/app/thaleia/id1581369776}{\textit{https://apps.apple.com/in/app/thaleia/id1581369776}} }
          \resumeItemListStart
            \resumeItem{Created a music-tracking iOS application with an event-driven microservices architecture, utilizing Python automation and the Spotify API to deliver real-time music updates.}
            \resumeItem{Orchestrated automated scheduling via AWS CloudWatch and remote notifications through AWS Pinpoint.}
          \resumeItemListEnd 
          \vspace{-13pt}
          \resumeProjectHeading
          {\textbf{Deep Learning Agent, TD-Gammon} $|$ \emph{Python, PyTorch, NumPy, Deep Learning, RL}}{Mar. 2021}
          \resumeSubItem{Link - \href{https://github.com/OneUpWallStreet/TD-Gammon}{\textit{https://github.com/OneUpWallStreet/TD-Gammon}}}
          \resumeItemListStart
            \resumeItem{Reimplemented TD Gammon (G. Tesauro, 1995) using PyTorch, enabling a self-play reinforcement learning agent to achieve superhuman performance in Backgammon.}
            \resumeItem{Constructed the Backgammon engine from the ground up using Python, meticulously training the agent through an extensive dataset of over 300,000 self-play games.}
            \resumeItem{Designed intuitive win probability graphs and a user-friendly "move probability" interface using Matplotlib.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}



%-----------PUBLICATIONS-----------
\section{Publications}
    \resumeItemListStart
    \resumeItem{Cloud Computing Services for Mobile Applications (Swarom Muley, Dr. S.T. Patil)}
    \resumeItemListEnd
  \vspace{-13pt}

% % %-----------Something else -----------
% \section{Not Sure what this should be}
%     \resumeItemListStart
%     \resumeItem{Hello}
% %         \resumeItem{Firefox for iOS, Swift Programming Language \& Tabliss Chrome Extension}
%     \resumeItemListEnd
% %  \vspace{-13pt}


% %-----------OPEN SOURCE CONTRIBUTIONS-----------
% \section{Open Source Contributions}
%     \resumeItemListStart
%         \resumeItem{Firefox for iOS, Swift Programming Language \& Tabliss Chrome Extension}
%     \resumeItemListEnd
%  \vspace{-13pt}



%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Swift, Python, Golang, C++, C, Java, JavaScript, Typescript, Ruby, SQL, HTML/CSS, Node.js, C\#, Bash} \\
     \textbf{Frameworks/Tools}{: AWS, Shell, Travis, Linux, Docker, Azure, Jenkins, Kubernetes, GCP, CI/CD, Terraform, Ansible} \\
     \textbf{Misc.}{: MySQL, NoSQL, AWS S3, MS SQL, EKS, Redis, REST-API, PostgreSQL, Kafka, Git, Express, MongoDB, Oracle} \\
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------INVOLVEMENT---------------
% \section{Leadership / Extracurricular}
%     \resumeSubHeadingListStart
%         \resumeSubheading{Fraternity}{Spring 2020 -- Present}{President}{University Name}
%             \resumeItemListStart
%                 \resumeItem{Achieved a 4 star fraternity ranking by the Office of Fraternity and Sorority Affairs (highest possible ranking).}
%                 \resumeItem{Managed executive board of 5 members and ran weekly meetings to oversee progress in essential parts of the chapter.}
%                 \resumeItem{Led chapter of 30+ members to work towards goals that improve and promote community service, academics, and unity.}
%             \resumeItemListEnd
        
%     \resumeSubHeadingListEnd


\end{document}
